\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}

\title{Written part of the IT Project}
\author{Antoine Vallée}
\date{18/06/12}

\begin{document}
\maketitle
	\par In this page, I'll try to summarize all the things I've done and all the important moment of this project during the year.
    \par Emmanuel and Me met before the beginning of the year on the Internet, and we had already talked about being together for the group project. Then we discussed about the game in September, and started it really early in the year. At the end of November, we had to find a third member, who is Antoine Pietri. 
	\par Antoine wanted to create a game where the sound would modify the gameplay, and we wanted to create a Shoot them all in the space, so both ideas could be mixed together, and it became a great game. Antoine Pietri got some problems for getting "integrated" in the project, he didn't work a lot at the beginning, but at the end he did some good things. Too bad he is a bit big headed.
	\par But, problems were also coming from me and Emmanuel, it's sometime hard to work with a friend, and it can leads to insults. But even if there were some accidents like these, we realised a great game and I do think that everyone achieved his work. For my part, I helped Emmanuel in developing the "beginning" of the game, and then I had to focus on graphics for a while. (So boring..).
	\par But the most interesting parts I worked on was the HUD, which is very important in a game like our; the IA, implemented through the bosses that you will be able to see in the game, and the level editor, which has taken me a long long long time to achieve, and to debug. The Menu wasn't a cool part too, but finally it's not so bad.
	\par I really enjoyed working on this project, and it was great to develop a huge project from scratch to the end. Developping a game is also a good thing, and I'm really proud to present the game to my friends when they ask me about my projects in Epita. If I had to change something, or to fix some errors we did at the beginning, I think that will not let Emmanuel be a project leader anymore, too bad at it; and I'll never accept anymore to work on graphics in a game. I really hate it.
	\par But after all, things didn't go so bad, finally we achieved a great project, we always got good marks at our presentations, and we were never late on anythings we had to develop.
\end{document}
