\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}

\title{Written part of the IT Project}
\author{Antoine Pietri}
\date{17/06/12}

\begin{document}
\maketitle
	\par This page is a short summary of what happened during the first three presentations
	of the project from my point of view.
	\par To give a little context, I first have to say that I wasn't here in the first days of this group, because I have been ``recruited'' in about November. I absolutely wanted to make something related to sound analysis because it uses a lot of signal processing and advanced mathematical concepts.
	\par When Emmanuel and Antoine decided to take me in their group, they also had
	a precise version of what the finished project should be, and they thought adding another part with sound analysis would be interesting, but they didn't want to work on it.
	\par For the first presentation, they also had a well-working game so I didn't really know what to do. I had to change the sound engine, so I made a front-end of the FMOD library and I made every music of the game use it. Then I displayed a sound spectrum on the game screen, to show that the sound analysis had begun.
	\par For the second presentation, I did a lot of research but I hadn't a lot of things to show, so I also corrected and improved the particle engine. I eventually achieved to calculate the ''sound energy`` at every instant of the game, which changed the speed of it.
	\par For the third presentation, I worked hard to implement a beat detection algorithm and the free mode based on it, at last a visible result of all my research (and maybe I'm a little too proud of it). Antoine managed to add new bosses and began the level editor while Emmanuel added new enemies. I personally think they didn't realised how hard making the beat detection algorithm was, and I assume that's why they don't take my work seriously : it's simply not very apparent, and their lack of interest make them to find that part boring.
	\par Finally for the last presentation, we all had to finalize the game. I personally added some new features to the interface and improved a lot my beat detection algorithm (and helped them to fix things they broke), while they were adding new content.
	\par Oh, and I also wrote the quasi-totality of all the reports, that's why I'm so tired\ldots No, I'm joking, you already know that I don't sleep anyway.
\end{document}
